The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-07-04 donde.tex
add loan as predictor in narrow and wide forest

Restrictions of choice are often surreptitiously imposed on consumers. Firms limit their worker's freedom by requiring time-consuming progress reports,  schools impose deadlines and pop quizzes, and loan contracts often require monthly repayment. As pointed out by \cite{Laibson2018}, although these choice-restricting mechanisms may be beneficial to firms and clients, they are often disliked by the latter, and therefore ‘shrouded’ by firms, i.e. not advertised but nonetheless embedded in products. \cite{Laibson2018} coins the term ``private paternalism'' for cases when restrictions on the freedom of choice is implemented by a firm in a way that advances a client's interests.

Substantiating a case for private paternalism is not easy. It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose it. Because choice may be correlated with unobservables, identification 
is challenging in observational studies.  %This is not a straightforward task because choice will be driven by unobservable factors, and to address the question fully 
Moreover, to have a complete picture of the benefits of forcing, one would want a counterfactual for the outcome of both choosers and non-choosers. A large behavioral literature has illustrated that allowing borrowers or savers to choose commitment-style products increase savings in an Intention-to-Treat sense \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature has rarely inquired about the benefits of imposing commitment.\footnote{Selection on gains has such wide acceptance that economists often impose it in their models (for example, in the study of migration \cite{chiquiar2005international} and occupational choice \cite{heckman1990empirical}. In microfinance, a context close to ours, \citep{Murdoch} claims that positive selection exists, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.}  In this paper we illustrate how a three-armed, `controlled choice' design can be used to form counterfactuals for both choosers and non-choosers of commitment. We implement such a design in a high-stakes and policy-relevant environment, enabling us to test selection-on-gains as well as isolating the impact of paternalistic policies.

@@

We study the benefits of private paternalism in the context of pawnbroker lending. Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a 43 billion dollar industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.

Our collaborating pawn lender (henceforth Lender P) gave 70\% of the value of the pawn in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due at no penalty. We call this the status-quo contract. This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months for a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid). While an older literature considers the exploitative potential in over-collateralization and underpricing of collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.  %When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments. 
To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment features to induce default in a manner not obvious to borrowers. Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.

@@

Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of payment structure in pawn repayment contracts. Our control arm illustrates the costs of the status quo contract; fully \textcolor{blue}{56\%} of borrowers default and so lose their pawn.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a `commitment choice’ arm, in which borrowers are able at the time of taking a loan to opt into a structured repayment contract, in which they are asked to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, and borrowers levied a nominal fee of 2\% of that month's payment in case of delinquency as a reminder/reinforcement of the importance of these interim payments. In addition, we include a `forced commitment’ arm, in which all borrowers are required to repay using the monthly payment structure. We will use the terms monthly payments, structured payments, and commitment contract interchangeably.

We call this randomization of voluntary and forced commitment a controlled choice design, and it allows us to address several key questions.  First, does using more structured repayment contracts help pawnshop borrowers to save on financing cost. Second, do borrowers recognize this benefit and demand commitment? % demanding commitment in sufficient numbers?  
Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the Treatment on the Treated (ToT), the Treatment on the Untreated (TuT), and the average selection on gains.

Our results suggest that the structure of the commitment is strongly effective in preventing default, with the average individual in the forced arm paying financing costs inclusive of fees that are \hl{20\%} lower than the control, while default decreases by 6.5 percentage points (15\% of the mean). In terms of Annual Percentage Rates, the financial cost of borrowing is reduced by 34 percentage points. That is, imposing a commitment structure it is possible to save borrowers money by charging them fees. These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using the subjective instead of the gold value of the pawn, and imputing some adjustment for liquidity lost by requiring monthly payments.

The monthly payment contract seems to be achieving these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not, saving the later payments towards recovery (which are lost in the case of default). In the treatment group, the first payment occurs 13 days earlier, and the fraction recovering on the first visit by is 7.9 percentage points higher. The commitment contract also decreases fraction of borrowers making a payment and not recovering by 7 percentage points. Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. Instead, the commitment contract induces people who would otherwise pay something towards recovery to pay more and faster, as well as inducing others who would have made partial payments and anyways defaulted to instead pay nothing.  Both groups save money.

In spite of a large average treatment effect documenting financial cost savings, given the opportunity in the choice arm, only 11\% of borrowers actually choose payment structure. If the effect of payment structure were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had. However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}. Can the borrowers who did not choose commitment be those who simply don’t need it? We address this question by sequentially imposing more structure in the problem.

We start by not imposing assumptions and bounding the distribution of individual treatment effects as in \cite{fan2010sharp}. Using bounds we find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand the structured payment contract even though the treatment effect would be positive for them. Then, we impose the twin exclusion restrictions necessary for estimation of the ToT and TuT ---that the effect of choosing or not choosing is the same as being assigned or not assigned the contract, i.e. that the act of choosing itself is irrelevant.\footnote{This is a frequently used assumption even if often implicit. For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.}  With these assumptions, both treatment effects are point identified, as is the average selection on gains, the average selection on levels, and the average selection bias.  Our results indicate that while selection on gains are present in our sample, the financial cost savings of the TuT is still large (at \$356 pesos, it is equivalent to 24 percentage point savings in APR). Hence, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{While our estimated ToT is roughly twice the TuT, it is imprecisely estimated due to the low compliance rate, and the hypothesis of ToT=TuT is rejected only with 13 percent confidence for the APR and 12 percent confidence for default.}  We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e. the average selection bias is negative). Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that more than \hl{70\%} of would-be non-choosers would save on financial cost by being assigned to frequent payments. That is, the benefits of imposing a monthly payment are distributed broadly. \hl{TuT benefits are particularly large for XXX CHARACTERISTICS, and ToT benefits for those with XXX.}

%\textcolor{brown}{In a final step, we use the Causal Random Forest algorithm of \cite{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.  93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.} \textcolor{blue}{Targeting frequent payment products to those that benefit the most is a policy that should be explored. In this context we calculate \hl{XXX}.}

@@

What explains the persistence of a contract so contrary to borrowers’ interests?  First, we investigate whether simple impatience could explain the dissonance (our formula for financial does not use discounting, and the contract features near-term costs in return for longer-term benefits).  A simple simulation exercise suggests that at discount rates up to 4,000 percent per annum our core impacts on financial cost remains significantly negative, suggesting that discounting is unlikely to explain our results.  Next, we look at time inconsistent preferences, the workhorse behavioral explanation for the benefits of commitment.  In our context, not only is time inconsistency only a weak driver of selection into commitment, but the TuT of forcing commitment arises almost entirely among those who are \textit{not} time inconsistent.\footnote{\textcolor{blue}{Although telling, we acknowledge that our measure of present bias is simple (as its survey-based and the survey was necessarily short). For this reason this result needs to be interpreted with care.}}  In this pawnbroking sample we document substantial levels of over-optimism among borrowers, and it has predictive power for our results. %which we believe explains our results. 
Not only do 74\% of borrowers say that they will recover their pawn with perfect certainty (whereas only 43\% actually do), but the impact of forcing on those who would not choose commitment is almost perfectly confined to the sub-sample who reported sure confidence in recovery. Hence, in this context it appears that the explanation for low demand for commitment among those who benefit arises from an incorrect belief that one has no need to work to avoid default.

%Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.\footnote{More generally \hl{demand for commitment is higher among those with XXX characteristics.}}  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico. The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.

%do we want this paragraph on learning?
Does learning eventually overcome the low demand for commitment? For learning to happen clients would need to experiment the frequent payment contract, and this was not the typical contract in the industry. But even if the contract was experienced, borrowers may fail to learn or learn only slowly. We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat customers than those assigned to the status-quo contract. One way to interpret this is \textcolor{blue}{as `learning they like pawn-borrowing', i.e. having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they like pawning and pawn more.}\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one. This second explanation is unlikely since borrowers obtain a second loan not within the first 90 days of the first loan when payments are due; moreover, the correlation is also present conditional on having paid down the first loan. Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation. \textcolor{blue}{A different test, about `learning they like monthly-payments'} is whether conditional on coming again, clients would choose frequent payments. We test this and we cannot reject that demand is \textit{not} higher after experiencing the monthly payment contract, \textcolor{blue}{consistent with no learning or slow learning that the monthly payment contract is better than the status quo contract}, however sample sizes are small and \hl{the minimum detectable effect is XXX.}} %\textcolor{blue}{making this more rigorous test of learning inconclusive and left for future research. Having said this, after more than 100 years in operation, the biggest pawn lender in Mexico and most others still do not offer structured payment contracts.}

@@

%Replace this paragraph with discussion of optimal targeting of paternalism
Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates. By over-collateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate. We hesitate to give precise policy recommendations since we don't have good measures of welfare. Even though the monthly payment contract dramatically reduces financial cost, it could potentially generate lower (or higher) anxiety. Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate. \hl{Note also that since the fee for skipping payment is 2\% of the payment due, the illiquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.

@@

Our paper speaks to several strands of the literature.   First, we contribute methodologically to the large literature on treatment effect heterogeneity by showing how an experimental design with two forcing arms and one choice arm allows for identification of the ToT, the TuT and other important parameters under minimal assumptions.  A large literature inspired by \cite{heckman1979sample} and \cite{angrist1996identification} has used an exclusion restriction to instrument for the LATE; rarer are studies that have compared forcing to choice to instrument for the TUT (such as looking at compulsory high school requirements \citep{oreopoulos2006estimating}, and one at technology that defaults individuals into variable pricing of electricity \citep{fowlie2021default}.  When the three arms (control, choice, and forcing) are randomized in the same environment we gain a clear and policy-relevant window into how selection into treatment relates to heterogeneity in treatment effects.  This comparison of treatment effects across the compliance distribution is closely related to the evaluation of Marginal Treatment Effects, and hence speaks to the large observational literature using parametric assumptions and continuous instruments to estimate MTEs , such as \cite{heckman2007econometric} and \cite{cornelissen2018benefits}, and \cite{Walters}.

%\cite{aronow2013beyond} and \cite{angrist2013extrapolate} assume no selection on gains to estimate \hl{XXX}. \cite{Walters} achieve identification of the TuT by using parametric model and a distance instrument, which requires the model to be correct and the instrument

Second, we join a more nacent literature shedding light into private paternalism. In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies, and then find that demand for commitment is negatively correlated with such inconsistency. In the context of school choice, \cite{Walters} finds that students that select into more effective schools have smaller treatment effects from attending than those that select out. Besides being very different contexts from ours, we rely on very different methods. In contrast to \cite{Sprenger} we will directly point identify the TuT, obviating the need for elicitation of preferences to test for negative selection. In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument. \todo[inline]{FRANK, can we say something more precise than ``a structural model''?}

Finally, our results speak to the financial literature that examines the effect of contract structure on repayment.  While research in microfinance markets has not found the same benefits from providing a more regularized repayment environment \citep{Pande}, those experiments are performed on top of highly structured contracts and among borrower pools who may have selected into that type of lending precisely because it provides structure. This may explain why there is almost no default in the control group in \citep{Pande}. Second, we broaden the analysis of the extent to which voluntary commitment mechanisms are taken up and effective.  Like our study, commitment demand has been found to be low in a number of contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}). Other papers have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). But unlike all these papers we can point identify the benefit the non-takers would have had if they had taken up and the benefit for the takers, and thus can talk more rigorously about private paternalism in this context.

@@

@@

\paragraph{Most borrowers lose their pawn.} Our context is also one with high borrower default: \hl{60\%} of clients lose their pawn in a time span of 230 days from the date of pawning. One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn, 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.  Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

\paragraph{Who chooses commitment?}

A natural starting point for understanding the role of voluntary commitment is the determinants of choice.  Figure \ref{determinants_choose} provides coefficient plots for univariate and multivariate Linear Probability Models explaining takeup of commitment in the Choice arm.  Contrary to the standard behavioral motivations, none of our measures of self control predict takeup, neither the metric arising from the paired discounting questions (e.g. those who are more impatient over immediate rather than future delays), nor a simple survey question asking whether they are tempted to mis-use money in their financial lives.  Individuals who report having trouble paying bills are actually \textit{less} likely to take commitment, as are those who have pawned before.  The only determinant in this figure that represents something like sophistication is that those with more education are more likely, in both univariate and multivariate regressions, to choose commitment.  Overall, we observe few strong determinants of commitment choice and the story does not appear to be a behavioral one.

@@

%\todo[inline]{Add a column with losing pawn. What about re-pawning?}
%\todo[inline]{How did we decide to deal with censoring?}

@@

%\todo[inline]{I think the re-pawn table should only have 4 columns. Remove variables 3,4, and 7. In terms of the order: keep column 1, make 5 and 6  the new columns 2 and 3, and make the current column 2 the new column 4. I am goint to write the paragraphs assuming this.}

@@

%\subsection{Censoring of Loan Completion}

>>>>

Restrictions of choice are often surreptitiously imposed on consumers. Firms limit their worker's freedom by requiring time-consuming progress reports,  schools impose deadlines and pop quizzes, and loan contracts often require monthly repayment. As pointed out by \cite{Laibson2018}, although these choice-restricting mechanisms may be beneficial to firms and clients, they are often disliked by the latter, and therefore ``shrouded'' by firms, i.e. not advertised but nonetheless embedded in products. \cite{Laibson2018} coins the term ``private paternalism'' for cases when restrictions on the freedom of choice is implemented by a firm in a way that advances a client's interests.

Making a case for private paternalism is not easy. It involves comparing the causal effect of forcing a certain product characteristic against the effect of letting people choose it. Because choice may be correlated with unobservables, identifying these two effects is challenging in observational studies.  %This is not a straightforward task because choice will be driven by unobservable factors, and to address the question fully 
Moreover, painting a complete picture of the benefits of forcing requires requires counterfactuals for both choosers and non-choosers. A large behavioral literature has illustrated that allowing borrowers or savers to choose commitment-style products increase savings in an intention-to-treat (ITT) sense \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature has rarely addressed the benefits of imposing commitment.\footnote{Selection on gains has such wide acceptance that economists often impose it in their models} (Although the examples above are plausible, substantiating a case for private paternalism is not easy. It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose on that characteristic. This is not an easy task because a given person wither has or does not have choice, and because choice induces selection, potentially biasing causal estimates. A large behavioral literature has illustrated that allocating borrowers to a commitment-savings product increase savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature does not show that commitment would not be chosen by those that would benefit from it, that is, that the treatment effect on the untreated (TUT) is positive. In fact, selection on gains has such wide acceptance that economists often impose it in their models \hl{CITES}. In microfinance, a context close to ours, \citep{Murdoch} claim that there exists positive selection, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments. However, they are unable to show that borrowers indeed benefit or that they indeed positively select based on treatment effects.

@@

This paper studies the benefits of restricting choice in the context of pawnbroker lending. Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.

Our collaborating pawn lender (henceforth Lender P) gave 70\% of the value of the pawn in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due at no penalty. This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months for a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid). While an older literature considers the exploitative potential in over-collateralization and underpricing of collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.  %When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments. 
To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment features to induce default in a manner that is not obvious to borrowers. Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.

@@

Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of alternative payment structures in pawn repayment contracts. Our control arm illustrates the costs of the status quo contract: fully 57\% of borrowers default and so lose their pawn.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a ``commitment choice'' arm, in which borrowers can opt into a structured repayment contract at the time of taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, a nominal fee of 2\% of that month's payment in case of delinquency. This fee serves as a reminder and a means of reinforcing the importance of these interim payments. In addition, we include a ``forced commitment'' arm, in which all borrowers are \emph{required} to repay using the structured monthly contract that is offered on an opt-in basis in the commitment choice arm.

The combination of voluntary and forced commitment within the RCT allows us to address several key questions. First, do structured repayment contracts lower financial costs for pawnshop borrowers? Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?  Finally, and most uniquely given the presence of a forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment. In particular, we use the choice, control, and fored arms to point identify the Treatment on the Treated (TOT) and the Treatment on the Untreated (TUT) effects, along with the average selection on gains (ASG) and average selection bias (ASB).

Our results suggest that the structure of the commitment is strongly effective in preventing default, with the average individual in the forced arm paying financing costs inclusive of fees that are \hl{20\%} lower than the control, while default decreases by 6.5 percentage points (15\% of the mean). In terms of Annual Percentage Rates, the financial cost of borrowing is reduced by 34 percentage points. That is, imposing commitment structure it is possible to save borrowers money by charging them fees! These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using the subjective instead of the gold value of the pawn, and imputing some adjustment for liquidity lost by requiring monthly payments.

The monthly payment contract seems to be achieving these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not, saving the later payments towards recovery. In the treatment group, the first payment occurs 13 days earlier, the fraction recovering on the first visit by is 7.9 percentage point higher. Commitment contract decreases fraction of borrowers making a payment and not recovering by 7 percentage points. \hl{Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. That is, the commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster, making them more likely to recover their pawn at a lower financial cost.}

In spite of a large average treatment effect documenting financial cost savings, given the opportunity in the choice arm, only 11\% of borrowers actually choose commitment. If the effect of commitment were homogeneous, this would be enough to conclude that the 89\%
who did not choose it would have been financially better off if they had. However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}. Can the borrowers who did not choose commitment be those who simply don’t need it? We address this question by sequentially imposing more structure in the problem.

\hl{We start by bounding the distribution of treatment effects $Y_{1i}-Y_{0i}$ using the two marginal distribution } in the treatment and control arms as in \cite{fan2010sharp}. We find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand even though the treatment effect would be positive for them. Then, we impose the mild exclusion restriction that the effect of the contract does not depend on how they got it, that is: choosing a contract has the same treatment effect as being assigned to the contract.\footnote{This is a frequently used assumption even if often implicit. For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.} We show that in this case our 3-armed experiment point identifies the TuT. We then estimate that the financial cost savings of the TuT is large, at \$356 pesos, equivalent to 24 percentage point savings in APR. That is, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{We estimate a positive TOT that is larger than the TuT, but it is imprecise\footnote{This results from the smaller sample size, given that few chose the monthly payment contract.}, and the hypothesis of TOT=TUT is rejeted only with 13 percent confidence for the APR and 12 percent confidence for default.}  We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e. the average selection bias is negative). Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that \hl{70\%} of would-be non-choosers would save on financial cost by being assigned to frequent payments. That is, the benefits of imposing a monthly payment are distributed broadly. \hl{TuT benefits are particularly large for XXX CHARACTERISTICS, and TOT benefits for those with XXX.}

\textcolor{brown}{In a final step, we use the Causal Random Forest algorithm of \cite{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.  93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.} \textcolor{blue}{Targeting frequent payment products to those that benefit the most is a policy that should be explored. In this context we calculate \hl{XXX}.}

@@

What explains the persistence of a contract so contrary to borrowers’ interests?  First, we show substantial levels of over-optimism among borrowers.  Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.\footnote{More generally \hl{demand for commitment is higher among those with XXX characteristics.}}  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico. The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.

Does learning eventually overcome the low demand for commitment? For learning to happen clients would need to experiment the frequent payment contract, and this was not the typical contract in the industry. But even if the contract was experienced, borrower may fail to learn or learn only slowly. We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat costumers than those assigned to the status-quo contract. One way to interpret this is that that having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they want to borrow more.\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one. This second explanation is unlikely since borrowers obtain a second loan not within the first 90 days of the first loan when payments are due; moreover, the correlation is also present conditional on having paid down the first loan. Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.} However, a stronger test of liking the monthly payment contract is whether conditional on coming again, they would choose frequent payments. We test this and we cannot reject that demand is not higher after experiencing the monthly payment contract, however sample sizes are small and \hl{the minimum detectable effect is XXX.}

@@

Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates. By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate. We hesitate to give precise policy recommendations since we don't have good measures of welfare. Even though the monthly payment contract dramatically reduces financial cost, it could potentially generate lower (or higher) anxiety. Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate. \hl{Note also that since the fee for skipping payment is 2\%, the iliquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.

@@

Our paper speaks to several strands of the literature.   %First, they suggest consequential ways in which different financial services draw client pools with distinct behavioral biases. 
First, to research in microfinance studying the effect of payment frequency.  While research in microfinance markets has not found the same benefits from providing a more regularized repayment environment \citep{Pande}, those experiments are performed on top of highly structured contracts and among borrower pools who may have selected into that type of lending precisely because it provides structure. This may explain why there is almost no default in the control group in \citep{Pande}. Second, we broaden the analysis of the extent to which voluntary commitment mechanisms are taken up and effective.  Like our study, commitment demand has been found to be low in a number of contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}). Other papers have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). But unlike all these papers we can point identify the benefit the non-takers would have had if they had taken up and the benefit for the takers, and thus can talk more rigorously about private paternalism in this context.

@@

Two recent papers that shed some light into private paternalism. In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies, and then find that demand for commitment is negatively correlated with such inconsistency. In the context of school choice, \cite{Walters} finds that students that select into more effective schools have smaller treatment effects from attending than those that select out. Besides being very different contexts from ours, we rely on very different methods. In contrast to \cite{Sprenger} we will directly point identify the TuT, obviating the need for elicitation of preferences to test for negative selection. In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument. \hl{FRANK, can I say something more precise than ``a structural model''?}

Methodologically we contribute to the large literature on treatment effect heterogeneity by showing how an experimental design with two forcing arms and one choice arm allows for identification of the TOT, the TUT and other important parameters under minimal assumptions. \cite{aronow2013beyond} and \cite{angrist2013extrapolate} assume no selection on gains to estimate \hl{XXX}. \cite{Walters} achieve identification of the TuT by using parametric model and a distance instrument, which requires the model to be correct and the instrument to be valid. TUT and ATE implied by LATE-and-re-weight differ sharply from his model-based estimates. The method of 
\cite{heckman2007econometric} and \cite{cornelissen2018benefits} require the availability of instrumental variable with rich support, and separability of observed and unobserved determinants of treatment effects.

@@

\paragraph{Most borrowers lose their pawn.} Our context is also one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning. One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn, 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.  Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

@@

\todo[inline]{Add a column with losing pawn. What about re-pawning?}
\todo[inline]{How did we decide to deal with censoring?}

@@

\todo[inline]{I think the re-pawn table should only have 4 columns. Remove variables 3,4, and 7. In terms of the order: keep column 1, make 5 and 6  the new columns 2 and 3, and make the current column 2 the new column 4. I am goint to write the paragraphs assuming this.}

@@

\subsection{Censoring of Loan Completion}
